Hierarchical Reverberation Mapping

### 2013-10-09 Paper/ms.tex
Defining CCF better

The cross-correlation function for a single object is defined as

\begin{eqnarray}
\textnormal{CCF}(\tau) &=&
\sum_{i=1}^{N_c} \sum_{j=1}^{N_l} \left(\frac{(y_i - \bar{y})(l_j - \bar{l})}{\sigma_{y_i}^2\sigma_{l_j}^2}\right)
\delta\left[\tau - (t_{l_j} - t_{y_i})\right]
\end{eqnarray}

>>>>

The cross-correlation function for a single object is defined as follows. First,
the mean levels $\bar{y}$ and $\bar{l}$ of the continuum and line light curves,
are calculated (weighted by the reported size of the error bars on each
measurement):
\begin{eqnarray}
\bar{y} &=& \frac{\sum_{i=1}^{N_c} \left(y_i/\sigma_{y_i}^2\right)}{\sum_{i=1}^{N_c} \left(1/\sigma_{y_i}^2\right)}\\
\bar{l} &=& \frac{\sum_{i=1}^{N_l} \left(l_i/\sigma_{l_i}^2\right)}{\sum_{i=1}^{N_l} \left(1/\sigma_{l_i}^2\right)}
\end{eqnarray}

The cross correlation function, as a function of lag $\tau$, is then defined as:
\begin{eqnarray}
\textnormal{CCF}(\tau) =
\sum_{i=1}^{N_c} \sum_{j=1}^{N_l}
\left(\frac{(y_i - \bar{y})(l_j - \bar{l})}{\sigma_{y_i}^2\sigma_{l_j}^2}
\delta\left[\tau - (t_{l_j} - t_{y_i})\right]\right)
\end{eqnarray}
This can be understood as a set of delta-function spikes, one for each pair
of points (one point chosen from the continuum data, and one point from the
line data). The position of each spike depends on the time between the continuum
data point and the line data point, and the mass of each spike is proportional
to the continuum and line fluxes.
